
### Setup and Inputs

```{r setup}

rm(list = ls())
gc()

library("tidyr")
library("lmerTest")
library("moments")
library("here")
library("ggplot2")
library("scales")
library("dplyr")
library("data.table")
library("tidymodels")
library("rsample")
library("finetune")
library("forcats")
library("vip")
library("xgboost")
library("pdp")
library("patchwork")

options(scipen=999)
options(width = 200)
options(DT.options = list(warn = FALSE))

```


```{r inputs}

# Get folder location of the data
folder_location <- here("data", "export")
model_folder <- here("data", "models")

# Read in the primary data used for Galvanic II modeling
source_df <- fread(here(folder_location, "ads_us.csv"))
full_df <- fread(here(folder_location, "ads_us_full.csv"))
emotion_df <- fread(here(folder_location, "ads_us_emotions.csv"))

# Preliminary preparation and defining columns for feature engineering
FIXED_COLUMNS <- c(
  "session_id", "session_in", "session_out", "phasic_ads", "ars_ads",
  "ads_comparison", "segment_number", "ad_position", "program_country",
  "age_average", "females_pct"
)
IDENT_COLUMNS <- c("session_id", "session_in", "session_out")

modeling_df <- source_df %>% 
  mutate(females_pct = females_pct / 100)

modeling_full_df <- full_df %>% 
  mutate(females_pct = females_pct / 100)

emotion_full_df <- emotion_df %>% 
  mutate(females_pct = females_pct / 100)

```


### Features Engineering

```{r skewness_check}

# Calculate skewness for all columns that require possible transformation
skewness_summary <- modeling_df %>% 
  select(-all_of(FIXED_COLUMNS)) %>% 
  select(where(is.numeric)) %>% 
  summarize(across(everything(), ~skewness(., na.rm = TRUE))) %>% 
  pivot_longer(everything(), names_to = "features", values_to = "skewness") %>% 
  mutate(abs_skewness = abs(skewness)) %>% 
  arrange(desc(abs_skewness))
skewness_summary

# Quick check on some of the skewed columns
ggplot(modeling_df, aes(x = filler)) +
  geom_histogram(fill = "steel blue") +
  xlab("filler") +
  ylab("Count") +
  ggtitle("Histogram of filler") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(label=comma)

ggplot(modeling_df, aes(x = ethnicity_EN)) +
  geom_histogram(fill = "steel blue") +
  xlab("ethnicity_EN") +
  ylab("Count") +
  ggtitle("Histogram of ethnicity_EN") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(label=comma)

ggplot(modeling_df, aes(x = neutrality_pct)) +
  geom_histogram(fill = "steel blue") +
  xlab("neutrality_pct") +
  ylab("Count") +
  ggtitle("Histogram of neutrality_pct") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(label=comma)

ggplot(modeling_df, aes(x = Dic_EN)) +
  geom_histogram(fill = "steel blue") +
  xlab("Dic_EN") +
  ylab("Count") +
  ggtitle("Histogram of Dic_EN") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(label=comma)

ggplot(modeling_df, aes(x = time)) +
  geom_histogram(fill = "steel blue") +
  xlab("time") +
  ylab("Count") +
  ggtitle("Histogram of time") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(label=comma)

```


```{r inflated_zero}

# Check for columns that have inflated zeroes
inflated_zeroes <- modeling_df %>% 
  select(-all_of(FIXED_COLUMNS)) %>% 
  select(where(is.numeric)) %>% 
  summarize(across(everything(), ~mean(.x == 0, na.rm = TRUE))) %>% 
  pivot_longer(everything(), names_to = "features", values_to = "zero_pct") %>% 
  arrange(desc(zero_pct))
inflated_zeroes

```


Data Transformation Rules:
  1.) Remove columns with ≥ 95% zeros
  2.) Convert columns with 80-95% zeros to binary
  3.) Calculate skewness on REMAINING continuous columns
  4.) Log-transform columns with skewness > 1
  5.) Reflection log-transform columns with skewness < -1


### Gradient Boosting - Full Dataset

```{r data_preparation}

# Define columns to leave out and the modify some of the other columns
remove_cols <- c("ads_comparison", "program_country")
xgb_df <- modeling_full_df %>% 
  select(-all_of(IDENT_COLUMNS)) %>% 
  select(-all_of(remove_cols))

# Split the data into training and testing sets
set.seed(3825)
phasic_split <- initial_split(xgb_df %>% select(-ars_ads), prop = 0.8, strata = phasic_ads)

set.seed(3825)
ars_split <- initial_split(xgb_df %>% select(-phasic_ads), prop = 0.8, strata = ars_ads)

phasic_train <- training(phasic_split)
phasic_test <- testing(phasic_split)

ars_train <- training(ars_split)
ars_test <- testing(ars_split)

```


```{r trainer_preparation}

# Create recipe for trainer
phasic_recipe <- recipe(phasic_ads ~ ., data = phasic_train) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE)
ars_recipe <- recipe(ars_ads ~ ., data = ars_train) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

# Create model spec for both trainers
xgb_spec <- boost_tree(
  trees = tune(),
  tree_depth = tune(),
  min_n = tune(),
  learn_rate = tune(),
  loss_reduction = tune(),
  sample_size = tune()
) %>% 
  set_engine("xgboost") %>% 
  set_mode("regression")

xgb_params <- xgb_spec %>% 
  extract_parameter_set_dials() %>% 
  update(
    trees = trees(range = c(100, 1000)),
    tree_depth = tree_depth(range = c(3, 10)),
    min_n = min_n(range = c(5, 40)),
    learn_rate = learn_rate(range = c(-2, -0.5)),
    loss_reduction = loss_reduction(range = c(-3, 1)),
    sample_size = sample_prop(range = c(0.5, 1.0))
  )

# Create the workflow used for both trainers
phasic_workflow <- workflow() %>% 
  add_recipe(phasic_recipe) %>% 
  add_model(xgb_spec)
ars_workflow <- workflow() %>% 
  add_recipe(ars_recipe) %>% 
  add_model(xgb_spec)

# Create cross-validation fold for both trainers
phasic_cv <- vfold_cv(phasic_train, v = 10, strata = phasic_ads)
ars_cv <- vfold_cv(ars_train, v = 10, strata = ars_ads)

```


```{r bayes_tuning}

# Create a helper function to save tuned XGBoost models
xgb_tuning <- function(workflow, resamples, param_info, cache_path, seed = 3825) {
  
  # Create the directory if needed
  cache_dir <- dirname(cache_path)
  if (!dir.exists(cache_dir)) {
    dir.create(cache_dir, recursive = TRUE)
    message("Created folder: ", cache_dir)
  }
  
  # Check cache
  if (file.exists(cache_path)) {
    message("Loading cached model from: ", cache_path)
    return(readRDS(cache_path))
  }
  
  # Run tuning
  message("Running Bayesian tuning...")
  set.seed(seed)
  tuned_result <- tune_bayes(
    workflow,
    resamples = resamples,
    initial = 15,
    iter = 30,
    param_info = param_info,
    metrics = metric_set(rmse, rsq),
    control = control_bayes(verbose = TRUE, no_improve = 10)
  )
  
  # Save and return
  saveRDS(tuned_result, cache_path)
  message("Saved tuned model to: ", cache_path)
  return(tuned_result)
  
}

# Tune models and save as cache
phasic_tuned <- xgb_tuning(
  phasic_workflow,
  phasic_cv,
  xgb_params,
  here(model_folder, "phasic_tuned.rds")
)

ars_tuned <- xgb_tuning(
  ars_workflow,
  ars_cv,
  xgb_params,
  here(model_folder, "ars_tuned.rds")
)

```


```{r model_selection}

# Select best parameters and create workflow
phasic_params <- select_best(phasic_tuned, metric = "rmse")
phasic_selected <- finalize_workflow(phasic_workflow, phasic_params)

ars_params <- select_best(ars_tuned, metric = "rmse")
ars_selected <- finalize_workflow(ars_workflow, ars_params)

# Fit the final models
xgb_phasic <- fit(phasic_selected, data = phasic_train)
xgb_ars <- fit(ars_selected, data = ars_train)

```


```{r variable_importance}

# Extract variable importance out into a table
phasic_importance <- xgb_phasic %>% extract_fit_parsnip() %>% vi() %>% arrange(desc(Importance))
ars_importance <- xgb_ars %>% extract_fit_parsnip() %>% vi() %>% arrange(desc(Importance))

# Plot out the variable importance graphs
phasic_importance %>%
  head(20) %>%
  ggplot(aes(x = reorder(Variable, Importance), y = Importance)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Phasic Ads: Top 20 Important Features",
    x = NULL,
    y = "Importance (Gain)"
  ) +
  theme_minimal()

ars_importance %>%
  head(20) %>%
  ggplot(aes(x = reorder(Variable, Importance), y = Importance)) +
  geom_col(fill = "darkorange") +
  coord_flip() +
  labs(
    title = "Ars Ads: Top 20 Important Features",
    x = NULL,
    y = "Importance (Gain)"
  ) +
  theme_minimal()

```


### Gradient Boosting - Emotion Dataset

```{r data_preparation}

# Define columns to leave out and the modify some of the other columns
remove_cols <- c("ads_comparison", "program_country", "ads_duration")
xgb_df <- emotion_full_df %>% 
  filter(ads_duration >= 15000) %>%    # Filter to only ads that are more than 15 seconds long
  select(-all_of(IDENT_COLUMNS)) %>% 
  select(-all_of(remove_cols))

# Split the data into training and testing sets
set.seed(3825)
phasic_split <- initial_split(xgb_df %>% select(-ars_ads), prop = 0.8, strata = phasic_ads)

set.seed(3825)
ars_split <- initial_split(xgb_df %>% select(-phasic_ads), prop = 0.8, strata = ars_ads)

phasic_train <- training(phasic_split)
phasic_test <- testing(phasic_split)

ars_train <- training(ars_split)
ars_test <- testing(ars_split)

```


```{r trainer_preparation}

# Create recipe for trainer
phasic_recipe <- recipe(phasic_ads ~ ., data = phasic_train) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE)
ars_recipe <- recipe(ars_ads ~ ., data = ars_train) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

# Create model spec for both trainers
xgb_spec <- boost_tree(
  trees = tune(),
  tree_depth = tune(),
  min_n = tune(),
  learn_rate = tune(),
  loss_reduction = tune(),
  sample_size = tune()
) %>% 
  set_engine("xgboost") %>% 
  set_mode("regression")

xgb_params <- xgb_spec %>% 
  extract_parameter_set_dials() %>% 
  update(
    trees = trees(range = c(100, 1000)),
    tree_depth = tree_depth(range = c(3, 10)),
    min_n = min_n(range = c(5, 40)),
    learn_rate = learn_rate(range = c(-2, -0.5)),
    loss_reduction = loss_reduction(range = c(-3, 1)),
    sample_size = sample_prop(range = c(0.5, 1.0))
  )

# Create the workflow used for both trainers
phasic_workflow <- workflow() %>% 
  add_recipe(phasic_recipe) %>% 
  add_model(xgb_spec)
ars_workflow <- workflow() %>% 
  add_recipe(ars_recipe) %>% 
  add_model(xgb_spec)

# Create cross-validation fold for both trainers
phasic_cv <- vfold_cv(phasic_train, v = 10, strata = phasic_ads)
ars_cv <- vfold_cv(ars_train, v = 10, strata = ars_ads)

```


```{r hyperparameters_tuning}

# Tune models and save as cache
phasic_tuned <- xgb_tuning(
  phasic_workflow,
  phasic_cv,
  xgb_params,
  here(model_folder, "phasic_emotion_tuned.rds")
)

ars_tuned <- xgb_tuning(
  ars_workflow,
  ars_cv,
  xgb_params,
  here(model_folder, "ars_emotion_tuned.rds")
)

```


```{r model_selection}

# Select best parameters and create workflow
phasic_params <- select_best(phasic_tuned, metric = "rmse")
phasic_selected <- finalize_workflow(phasic_workflow, phasic_params)

ars_params <- select_best(ars_tuned, metric = "rmse")
ars_selected <- finalize_workflow(ars_workflow, ars_params)

# Fit the final models
xgb_phasic <- fit(phasic_selected, data = phasic_train)
xgb_ars <- fit(ars_selected, data = ars_train)

```


```{r variable_importance}

# Extract variable importance out into a table
phasic_importance <- xgb_phasic %>% extract_fit_parsnip() %>% vi() %>% arrange(desc(Importance))
ars_importance <- xgb_ars %>% extract_fit_parsnip() %>% vi() %>% arrange(desc(Importance))

# Plot out the variable importance graphs
phasic_importance %>%
  head(20) %>%
  ggplot(aes(x = reorder(Variable, Importance), y = Importance)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Phasic Ads: Top 20 Important Features",
    x = NULL,
    y = "Importance (Gain)"
  ) +
  theme_minimal()

ars_importance %>%
  head(20) %>%
  ggplot(aes(x = reorder(Variable, Importance), y = Importance)) +
  geom_col(fill = "darkorange") +
  coord_flip() +
  labs(
    title = "Ars Ads: Top 20 Important Features",
    x = NULL,
    y = "Importance (Gain)"
  ) +
  theme_minimal()

```


### Random Effect Model + XGB

```{r random_effect}

# Prepare the data to fit a random effect model
random_df <- modeling_full_df %>% 
  select(
    session_id, session_in, session_out, phasic_ads, ars_ads, segment_number,
    ad_position, program_format, age_average, females_pct
  ) %>% 
  mutate(program_format = fct_relevel(program_format, "Sports", "Scripted", "Unscripted"))

# Fit LMER to control for fixed effects
control_phasic <- lmer(
  phasic_ads ~ segment_number + ad_position + program_format + 
    age_average + females_pct + (1 | session_id),
  data = random_df
)
summary(control_phasic)

control_ars <- lmer(
  ars_ads ~ segment_number + ad_position + program_format + 
    age_average + females_pct + (1 | session_id),
  data = random_df
)
summary(control_ars)

# Add the residuals back into the dataset
random_df <- random_df %>% 
  mutate(
    "phasic_resid" = residuals(control_phasic),
    "ars_resid" = residuals(control_ars)
  )

```


```{r data_preparation}

# Define columns to leave out and the modify some of the other columns
remove_cols <- c(
  "ads_comparison", "program_country", "segment_number", "ad_position",
  "program_format", "age_average", "females_pct", "phasic_ads", "ars_ads"
)
xgb_df <- modeling_full_df %>%
  left_join(
    random_df %>% select(session_id, session_in, session_out, phasic_resid, ars_resid),
    by = c("session_id", "session_in", "session_out")
  ) %>% 
  select(-all_of(IDENT_COLUMNS)) %>% 
  select(-all_of(remove_cols))

# Split the data into training and testing sets
set.seed(3825)
phasic_split <- initial_split(xgb_df %>% select(-ars_resid), prop = 0.8, strata = phasic_resid)

set.seed(3825)
ars_split <- initial_split(xgb_df %>% select(-phasic_resid), prop = 0.8, strata = ars_resid)

phasic_train <- training(phasic_split)
phasic_test <- testing(phasic_split)

ars_train <- training(ars_split)
ars_test <- testing(ars_split)

```


```{r trainer_preparation}

# Create recipe for trainer
phasic_recipe <- recipe(phasic_resid ~ ., data = phasic_train) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE)
ars_recipe <- recipe(ars_resid ~ ., data = ars_train) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

# Create model spec for both trainers
xgb_spec <- boost_tree(
  trees = tune(),
  tree_depth = tune(),
  min_n = tune(),
  learn_rate = tune(),
  loss_reduction = tune(),
  sample_size = tune()
) %>% 
  set_engine("xgboost") %>% 
  set_mode("regression")

xgb_params <- xgb_spec %>% 
  extract_parameter_set_dials() %>% 
  update(
    trees = trees(range = c(100, 1000)),
    tree_depth = tree_depth(range = c(3, 10)),
    min_n = min_n(range = c(2, 20)),            
    learn_rate = learn_rate(range = c(-3, -1)),
    loss_reduction = loss_reduction(range = c(-7, -2)),
    sample_size = sample_prop(range = c(0.5, 1.0))
  )

# Create the workflow used for both trainers
phasic_workflow <- workflow() %>% 
  add_recipe(phasic_recipe) %>% 
  add_model(xgb_spec)
ars_workflow <- workflow() %>% 
  add_recipe(ars_recipe) %>% 
  add_model(xgb_spec)

# Create cross-validation fold for both trainers
phasic_cv <- vfold_cv(phasic_train, v = 10, strata = phasic_resid)
ars_cv <- vfold_cv(ars_train, v = 10, strata = ars_resid)

```


```{r hyperparameters_tuning}

# Tune models and save as cache
phasic_tuned <- xgb_tuning(
  phasic_workflow,
  phasic_cv,
  xgb_params,
  here(model_folder, "phasic_tuned_control.rds")
)

ars_tuned <- xgb_tuning(
  ars_workflow,
  ars_cv,
  xgb_params,
  here(model_folder, "ars_tuned_control.rds")
)

```


```{r model_selection}

# Select best parameters and create workflow
phasic_params <- select_best(phasic_tuned, metric = "rmse")
phasic_selected <- finalize_workflow(phasic_workflow, phasic_params)

ars_params <- select_best(ars_tuned, metric = "rmse")
ars_selected <- finalize_workflow(ars_workflow, ars_params)

# Fit the final models
xgb_phasic <- fit(phasic_selected, data = phasic_train)
xgb_ars <- fit(ars_selected, data = ars_train)

```


```{r variable_importance}

# Extract variable importance out into a table
phasic_importance <- xgb_phasic %>% extract_fit_parsnip() %>% vi() %>% arrange(desc(Importance))
ars_importance <- xgb_ars %>% extract_fit_parsnip() %>% vi() %>% arrange(desc(Importance))

# Plot out the variable importance graphs
phasic_importance %>%
  head(20) %>%
  ggplot(aes(x = reorder(Variable, Importance), y = Importance)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Phasic Ads: Top 20 Important Features",
    x = NULL,
    y = "Importance (Gain)"
  ) +
  theme_minimal()

ars_importance %>%
  head(20) %>%
  ggplot(aes(x = reorder(Variable, Importance), y = Importance)) +
  geom_col(fill = "darkorange") +
  coord_flip() +
  labs(
    title = "Ars Ads: Top 20 Important Features",
    x = NULL,
    y = "Importance (Gain)"
  ) +
  theme_minimal()

```


```{r pdp_analysis}

# Extract the fitted model from your workflow
phasic_fit <- extract_fit_parsnip(xgb_phasic)
ars_fit <- extract_fit_parsnip(xgb_ars)

# Prep training data through the recipe
phasic_baked <- phasic_recipe %>% prep() %>% bake(new_data = phasic_train)
ars_baked <- ars_recipe %>% prep() %>% bake(new_data = ars_train)

# Helper function to generate PDP plots
generate_pdp_plots <- function(fit, baked_data, target_col, features, color) {
  pdp_plots <- lapply(features, function(feat) {
    partial(
      fit$fit,
      pred.var = feat,
      train = as.data.frame(baked_data %>% select(-all_of(target_col))),
      plot = FALSE
    )
  })
  
  plot_list <- lapply(seq_along(features), function(i) {
    ggplot() +
      geom_line(data = pdp_plots[[i]], 
                aes(x = .data[[features[i]]], y = yhat),
                color = color, linewidth = 1) +
      geom_rug(data = baked_data, 
               aes(x = .data[[features[i]]]),
               alpha = 0.1, sides = "b") +
      labs(title = features[i], y = "Partial Dependence") +
      theme_minimal()
  })
  
  wrap_plots(plot_list, ncol = 3)
}

# Phasic PDP
phasic_tone_features <- c(
  "neutrality_pct", "shehe", "happiness_pct", "reward_EN",
  "Culture_EN", "Conversation_EN", "affiliation_EN", "sadness_pct"
)
generate_pdp_plots(phasic_fit, phasic_baked, "phasic_resid", phasic_tone_features, "steelblue")

# Ars PDP
ars_tone_features <- c(
  "health", "wc", "avg_valence", "det_EN", "illness_EN",
  "neutrality_pct", "function_EN", "politic_EN", "happiness_pct"
)
generate_pdp_plots(ars_fit, ars_baked, "ars_resid", ars_tone_features, "darkorange")

```


### Roberta Testing

```{r roberta_fit}

# Define columns to leave out and the modify some of the other columns
remove_cols <- c(
  "ads_comparison", "program_country", "segment_number", "ad_position",
  "program_format", "age_average", "females_pct", "phasic_ads", "ars_ads",
  "ads_duration"
)
xgb_df <- emotion_full_df %>%
  left_join(
    random_df %>% select(session_id, session_in, session_out, phasic_resid, ars_resid),
    by = c("session_id", "session_in", "session_out")
  ) %>% 
  select(-all_of(IDENT_COLUMNS)) %>% 
  select(-all_of(remove_cols))

phasic_train <- xgb_df %>% select(-ars_resid)
ars_train <- xgb_df %>% select(-phasic_resid)

# Create recipe for trainer
phasic_recipe <- recipe(phasic_resid ~ ., data = phasic_train) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE)
ars_recipe <- recipe(ars_resid ~ ., data = ars_train) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

# Create model spec for both trainers
xgb_spec <- boost_tree(
  trees = tune(),
  tree_depth = tune(),
  min_n = tune(),
  learn_rate = tune(),
  loss_reduction = tune(),
  sample_size = tune()
) %>% 
  set_engine("xgboost") %>% 
  set_mode("regression")

xgb_params <- xgb_spec %>% 
  extract_parameter_set_dials() %>% 
  update(
    trees = trees(range = c(100, 1000)),
    tree_depth = tree_depth(range = c(3, 10)),
    min_n = min_n(range = c(2, 20)),            
    learn_rate = learn_rate(range = c(-3, -1)),
    loss_reduction = loss_reduction(range = c(-7, -2)),
    sample_size = sample_prop(range = c(0.5, 1.0))
  )

# Create the workflow used for both trainers
phasic_workflow <- workflow() %>% 
  add_recipe(phasic_recipe) %>% 
  add_model(xgb_spec)
ars_workflow <- workflow() %>% 
  add_recipe(ars_recipe) %>% 
  add_model(xgb_spec)

# Create cross-validation fold for both trainers
phasic_cv <- vfold_cv(phasic_train, v = 10, strata = phasic_resid)
ars_cv <- vfold_cv(ars_train, v = 10, strata = ars_resid)

# Tune models and save as cache
phasic_tuned <- xgb_tuning(
  phasic_workflow,
  phasic_cv,
  xgb_params,
  here(model_folder, "phasic_emotion_control.rds")
)

ars_tuned <- xgb_tuning(
  ars_workflow,
  ars_cv,
  xgb_params,
  here(model_folder, "ars_emotion_control.rds")
)

# Select best parameters and create workflow
phasic_params <- select_best(phasic_tuned, metric = "rmse")
phasic_selected <- finalize_workflow(phasic_workflow, phasic_params)

ars_params <- select_best(ars_tuned, metric = "rmse")
ars_selected <- finalize_workflow(ars_workflow, ars_params)

# Fit the final models
xgb_phasic <- fit(phasic_selected, data = phasic_train)
xgb_ars <- fit(ars_selected, data = ars_train)

# Extract variable importance out into a table
phasic_importance <- xgb_phasic %>% extract_fit_parsnip() %>% vi() %>% arrange(desc(Importance))
ars_importance <- xgb_ars %>% extract_fit_parsnip() %>% vi() %>% arrange(desc(Importance))

# Plot out the variable importance graphs
phasic_importance %>%
  head(20) %>%
  ggplot(aes(x = reorder(Variable, Importance), y = Importance)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Phasic Ads: Top 20 Important Features",
    x = NULL,
    y = "Importance (Gain)"
  ) +
  theme_minimal()

ars_importance %>%
  head(20) %>%
  ggplot(aes(x = reorder(Variable, Importance), y = Importance)) +
  geom_col(fill = "darkorange") +
  coord_flip() +
  labs(
    title = "Ars Ads: Top 20 Important Features",
    x = NULL,
    y = "Importance (Gain)"
  ) +
  theme_minimal()

```








